### 2015-07-30 Harris_2015/manuscript-materials/draft.Rmd
graphs

#### Twenty species.
The accuracy of the four evaluated methods varied substantially, depending on
the parameters that produced the simulated communities (Figure 3). In general,
however, there was a consistent ordering…

The three methods that estimated marginal relationships among species and did
not explicitly control for indirect species interactions (the null model, the
joint species distribution model’s correlation coefficients, and the sample
correlation coefficients) differed from one another in their $R^2$ values,
but their estimates were surprisingly similar to one another. In particular, the
correlation coefficients were extremely similar to the estimates  from the other
two methods (Spearman’s rho = X for the joint species distribution model’s
correlation matrix and Y for the null model).

@@

**Figure 3.**
Proportion of variance in interaction coefficients explained by each method
across varying numbers of sampled locations.

>>>>

#### Twenty species.
The accuracy of the evaluated methods varied substantially, depending on
the parameters that produced the simulated communities (Figure 3a). In general,
however, there was a consistent ordering.  The Markov network explained the
largest portion of the variance (34.6% overall), followed
by the generalized linear models (29.9%), partial correlations from the raw
presence-absence data (27.5%), and partial correlations from BayesComm, the joint
species distribution model (26.1).  The three methods that did not attempt to
control for indirect interactions all explained less than 20% of the variance.
Of these, the sample correlation matrix based on the raw data performed the best
(18.6%), followed by the null model (15.4) and BayesComm's correlation matrix
(11.6).

Although these last three methods had very different $R^2$ values, there was a
very close mapping between their estimates (after controlling for the size of
the simulated landscapes; Figure 3b).  This suggests that the correlation
matrices from joint species distribution models and especially the
effect sizes from null models contain essentially the same information that
could be obtained more easily by calculating correlation coefficients between
species' presence-absence vectors. This, in turn, demonstrates that these
methods do not effectively control for any indirect effects in the network.

@@

**Figure 3.**
**A.** Proportion of variance in interaction coefficients explained by each method
across varying numbers of sampled locations.
**B.** The $Z$-scores produced by the null model (i.e. the Pairs software) for
each pair of species are very predictable from the correlation between the
presence-absence vectors of those same species and from the number of sites on
the landscape.
